Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact

### 2024-08-12 mainReviewed.tex
Initial Overleaf Import

\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

@@

@@

\title*{Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Luca Berti, Laetitia Giraldi, Christophe Prud'homme, Céline Van Landeghem}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Luca Berti \at CNRS - Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg  \email{berti@math.unistra.fr}
\and Laetitia Giraldi \at Universit\'e C\^ote d'Azur, INRIA, CNRS, Calisto team, \email{laetitia.giraldi@inria.fr}
\and Christophe Prud'homme \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{christophe.prudhomme@math.unistra.fr}
\and Céline Van Landeghem \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{c.vanlandeghem@unistra.fr}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract{Swimming involves a body's capability to navigate through a fluid by undergoing self-deformations. Typically, fluid dynamics is described by Navier-Stokes equations, and when integrated with a swimming body, it results in a highly intricate model. This paper introduces a computational framework for simulating the movement of multiple swimmers with various geometries immersed in a Navier-Stokes fluid. The approach relies on the finite element method with an Arbitrary Lagrangian-Eulerian (ALE) framework to handle swimmer displacements. Numerous numerical experiments demonstrate the adaptability of the computational framework across various scenarios.
All the implementations are made using the \feelpp\ finite element library \cite{feelpp-ref}.}

@@

Swimming involves the capacity of a body to navigate through a fluid by undergoing self-deformations. Typically, the fluid dynamics is described by Navier-Stokes equations, and when coupled with a swimming body, it yields a highly intricate model. One of the main difficulties lies in the fact that the swimmers deform and move, requiring constant adjustment of the fluid domain and fluid-swimmer interface. Other difficulties come into play when accounting for obstacles, the possible presence of other swimmers, and the modeling of their interactions. These interactions are even more complex because disturbances caused by fluid agitation at one point in the domain can propagate throughout the entire domain.

@@

%BEM (Lefebvre - Maury - Kenta)
A numerical method that is widely used in the micro-swimming community is the boundary element method, that relies on the integral formulation of the Stokes equations to determine the fluid velocity field \cite{pozrikidis1992boundary}. 
This formulation reduces the computation cost of the dynamics of the swimmer by working on the swimmer's boundary alone, which ensures significant memory savings since the fluid domain is not discretized. 
The boundary integral formulation expresses the fluid velocity at the boundary of the swimmer as a function of fluid stresses and velocities, via the fundamental solutions of the Stokes equations. Since these functions exhibit singular behaviour when the source and evaluation points are close together, a regularisation procedure needs to be employed for the numerical solution. Several solutions are possible: a regularisation of the numerical approximation of the singular integrals using a semi-analytic procedure \cite{huang_cruse} or the use of regularised kernels \cite{Fauci}.

@@

% Méthode de frontière immergée
When inertial effects become more important and the low Reynolds number assumption is no longer valid, 
it is necessary to resort to the solution of the system coupling Navier-Stokes equations with Newton's equations for rigid bodies. 
A commonly used method involves approximating the values of fluid velocity and pressure on a fixed discretization of the domain and representing the swimmers using an implicit function that parameterizes their boundaries. 
These approaches are commonly referred to Immersed Boundary Methods with level set functions describing the swimmer. 
The challenge of these methods lies in following the swimmer. 
For instance, one may use methods called CutFEM (Cut Finite Element Method), which project the swimmer's boundary onto the fixed mesh.
the CUTFEM approach in which mesh intersections are computationally costly. \cite{Monasse,Iollo,bergmann2016bioinspired,hansbo2016cut,burman2015cutfem}
%[citer Laurent Monasse, Chouly, Iollo, Giocomini Matteo]

@@

% Méthode FEM-ALE
In this chapter, we discuss an alternative method to compute the displacement of multiple deformable swimmers immersed in a Navier-Stokes fluid, which can be confined within a geometrically complex domain. This method is based on the finite element solution of the swimming problem, using the Arbitrary-Lagrangian-Eulerian description for the motion of the fluid domain.
This approach is popular in fluid-structure interaction problems \cite{chabannes2013high,pena2012high}, and it is based on a formulation of the fluid equations in an intermediate frame between the Eulerian and Lagrangian description.
A characteristic of this method is that the solutions are approximated on a mesh that deforms over time, following the deformation and movements of the swimmers.
As the immersed boundary method, it accounts for the full, non-approximated description of the fluid dynamics.
This numerical method is very versatile and it has been used in a wide variety of contexts and physical problems, and it can be easily extended to cases in which the Newtonian fluid is substituted by a complex fluid, which is often the case of biological media.

@@

%Below, we present a dynamic system that describes the dynamics of a swimmer.
%la partie fluide :
We consider Navier-Stokes equations in a moving domain to describe the motion of a Newtonian fluid medium. 
Let $\CompDomain_t\subset \R^d$, where $d=2,3$ is the dimension, denote the region occupied by the fluid at time $t$, $\mu$  the constant fluid viscosity and $\Density$ the constant fluid density. Let $\Solid_t^i \subset \R^d$ be the domain that is occupied by the body $i$, $i = 1,...,N$, where $N$ the number of bodies, of constant density $\Density_s^i$. At each time instant $t$, the fluid is in contact with the swimmers, and $\bar{\CompDomain}_{t} \cap \bar{\Solid}_t^i = \partial \Solid_t^i$.
The notations are summarized in Figure \ref{fig:swimmer-tikz}.

The velocity field $\Vel(t,x):]0,T]\times \CompDomain_t \rightarrow \R^d$ and the pressure field $\Pres(t,x):]0,T]\times\CompDomain_t \rightarrow \R$ satisfy the Navier-Stokes equations given by: 
\begin{equation}
	\begin{aligned}
		\rho\Big(\partial_t \Vel +( \Vel \cdot \nabla )\Vel \Big) - \nabla \cdot \sigma(u,p) &= f%\nabla \cdot \Stress %\nabla \Pres + \Viscosity \Delta \Vel + f 
		\quad &\text{on $ ]0,T]\times \CompDomain_t$},
		\\
		\nabla \cdot \Vel &= 0  \quad&\text{on $ ]0,T]\times \CompDomain_t$},\\
		\Vel &= \bar{\Vel}^i% U + \Omega \times(x-\bar{x}) + u_d 
		\quad &\text{on $]0,T]\times \partial \Solid_t^i$},\\
		\Vel(0,x) &= \Vel_0(x) \quad &\text{on $ \{0\}\times\CompDomain_0$},\\
		\Vel(t,x) &= h(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,D}$},\\
		\sigma(u,p) \normal&= g(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,N}$},
	\end{aligned}
	\label{Eq:NS}
\end{equation}
where $\sigma(u,p)$ is the stress tensor $-\Pres\mathbb{I} + 2 \mu D(u)$ with $D(u) = \frac{1}{2}\left(\nabla u + (\nabla u)^T\right)$ and $\bar{\Vel}^i(t,x):[0,T]\times\partial \Solid_t^i \rightarrow \R^d$ results from the interaction between the fluid and the $i$-th swimmer's body and $f(t,x):[0,T]\times\CompDomain_t \rightarrow \R^d$ represents external volume forces. The function $u_0$ is the prescribed initial condition of the system. 
\begin{figure}
    \centering
\begin{center}
\begin{tikzpicture}

@@

\end{tikzpicture}
\end{center}
   \caption{Notations for the fluid model. $\CompDomain_t$ denotes the fluid domain and $\Solid^i_t,\Solid^j_t,\Solid^k_t$ denote the swimmers and solid objects included in the fluid. $\partial \Fluid_{t,N}$ and $\partial \Fluid_{t,D}$ denote the portions of the fluid boundary where Dirichlet and Neumann boundary conditions are prescribed.}
    \label{fig:swimmer-tikz}
\end{figure}
Here $h(t,x)$ and $g(t,x)$ represent the Dirichlet and Neumann boundary conditions, prescribed on the respective portions of the fluid boundary $ ]0,T]\times\partial\CompDomain_{t,D}$ and  $ ]0,T]\times\partial\CompDomain_{t,N}$, and we have that $\partial \CompDomain_{t} = \partial\CompDomain_{t,D} \cup \partial\CompDomain_{t,N} \cup \partial \Solid_t^i$, $i=1,...,N$, for all times.

In the case of swimming, $\bar{\Vel}^i$ can be split into two contributions. The first one is determined by the linear velocity $\tvel^i(t): [0,T]\to\R^d$ and angular velocity  $\angvel^i(t):[0,T]\to \R^{d^*}$ of the swimmer around its center of mass $\CenterMassi$, where $d^*=1$ if $d=2$ and $d^*=3$ if $d=3$, while the second one is given by the deformation velocity of the solid $\Vel_d^i$, if present. The function $\bar{u}^i$ then becomes $\bar{\Vel}^i(t,x) = \tvel^i(t) + \angvel^i(t)\times (x-\CenterMassi)+ \Vel_d^i(t)$.

@@

The swimmer's motion is either a result of its deformation, which generates hydrodynamic forces that are then translated into rigid movement through Newton's laws, or external forces such as gravity or collision forces.

Let us define the mass of the $i$-th swimmer be given by  $\mass^i = \int_\Solid \Density_{\Solid}^i$ %, let $\CenterMassi = \frac{1}{\mass^i} \int_{\Solid^i} \Density_{\Solid}^i x$ be its center of mass, 
and $\Inertia^i = \int_{\Solid^i} \Density_{\Solid}^i (x-\CenterMassi) \otimes (x-\CenterMassi)$ 
its positive definite and symmetric inertia tensor. 
The Newton and Euler equations describing the rigid body velocities $\tvel^i$ and $\angvel^i$ read:
\begin{equation}
	\begin{aligned}
		\mass^i \frac{d}{dt}\tvel^i &= F_e^i -\int_{\partial \Solid^i} \sigma \normal \,\textrm{ds},\\
		\frac{d}{dt}(\Rmat \Inertia^i \Rmat^T \angvel^i) &= T_e^i -\int_{\partial \Solid^i} \sigma \times (x-\CenterMassi)\,\textrm{ds}, 
	\end{aligned}
	\label{Eq:RB}
\end{equation}

where $\normal$ is the unit outward normal to $\partial \Solid^i$. The rotational speed $\angvel^i_k$ is linked with the orientation of the swimmer using

\begin{equation*}
	\begin{aligned}
		\frac{d}{dt} \Angle_k &= \angvel^i_k, \quad \text{for $k \in \{x,y,z\}$},\\
		\Rmat &=\Rmat_z(\Angle_z)\Rmat_y(\Angle_y)\Rmat_x(\Angle_x),
	\end{aligned}
\end{equation*}
where $R_k(\Angle_k)$ denotes the rotation matrix around axis $k \in \{x,y,z\}$ of 
angle $\Angle_k$. If $d=2$, $R(\theta)$ has the form: 
\begin{equation*}
	\begin{aligned}
		\Rmat(\Angle) &= \begin{bmatrix}
			\cos(\Angle) & \sin(\Angle)\\
			-\sin(\Angle) & \cos(\Angle)
		\end{bmatrix}.
	\end{aligned}
\end{equation*}
While in three dimensions:
$$	
	\Rmat_z(\Angle_z) = \begin{bmatrix}
		\cos(\Angle_z) & -\sin(\Angle_z) & 0\\
		\sin(\Angle_z) & \cos(\Angle_z)& 0 \\
		0& 0 & 1
	\end{bmatrix},
	\Rmat_y(\Angle_y) = \begin{bmatrix}
		\cos(\Angle_y) &0 & \sin(\Angle_y) \\
		0& 1& 0\\
		-\sin(\Angle_y) & 0& \cos(\Angle_y)
	\end{bmatrix},\\
$$
$$
	\Rmat_x(\Angle_x) = \begin{bmatrix}
		1 & 0 & 0\\
		0 &\cos(\Angle_x) & -\sin(\Angle_x) \\
		0 &\sin(\Angle_x) & \cos(\Angle_x) 
	\end{bmatrix}.
$$
The angle $\Angle$ belongs to  $\Theta$, with $\Theta = [-\pi,\pi]$ if $d=2$, 
or $\Angle_k \in \Theta$, for $k=x,y,z$, $\Theta=[-\pi,\pi]\times[0,\pi]\times[0,\pi/2]$ if $d=3$.

Equations \eqref{Eq:RB} correspond to the balance of forces and torques applied to each swimmer, stating that non-zero net contributions from fluid stresses $\sigma n$ or additional external forces $F_e^i$ and torques $T_e^i$ lead to velocity variations.

@@

In this subsection, we describe how a swimmer's collisions with solid obstacles, other swimmers (as active particles), and the boundaries of the fluid domain are handled. Our model is based on a short-range contact-avoidance repulsive force introduced by R. Glowinski in \cite{glowinski}, for which a collision zone of width $\rho$ is defined in which the forces are activated.
In equation \eqref{Eq:RB}, the external force and torque terms $F_e^i$ and $T_e^i$ summarize the physical interactions occurring when the distances $d_{ij}$ and $d_{i}$ between swimmer $i$ and another body $j$, or between swimmer $i$ and the domain boundary $\partial \Fluid_t$, are smaller than the width $\rho$ of the collision zone.  
The definition of the collision force for a swimmer-swimmer or swimmer-boundary pair is given by:

$$
\overrightarrow{F_{ij}} = - \epsilon A  \overrightarrow{X_i X_j }  1_{d_{ij} \leq \rho}, \qquad
\overrightarrow{F_{i \partial \Fluid_t}} = - \epsilon' A \overrightarrow{X_i X_{\partial \Fluid_t} }  1_{d_{i} \leq \rho}.
$$

@@

The total repulsion force applied on $\Solid^i$ is defined by:
$$
\overrightarrow{F_i} = \sum_{(i,j)|d_{ij} \leq \rho} \overrightarrow{F_{ij}} +  \sum_{i | d_i \leq \rho} \overrightarrow{F_{i \partial \Fluid_t}},
$$
where the first sum runs over all the body pairs $(i,j)$ such that $d_{ij}\le \rho$, and the second sum runs over all body-boundary pairs such that $d_{i}\le \rho$.

Force $\overrightarrow{F_i}$ leads to body rotations via its associated torque, defined by: 
$$
\overrightarrow{T_i} = - \overrightarrow{x_{CM}^i X_i} \times \overrightarrow{F_i},
$$
where $\overrightarrow{x_{CM}^i X_i}$ connects the center of mass of $\Solid^i$ and the contact point $X_i$ where $\overrightarrow{F_i}$ is applied.

The total repulsion force $\overrightarrow{F_i}$ and the external associated torque $T_i$ are added to  $F_e^i$ and $T_e^i$ in the Newton equation \eqref{Eq:RB}, thus modifying the trajectory of the swimmer.

@@

\subsection{The Arbitrary-Lagrangian-Eulerian formalism}
% Introduire le framework ALE --- DONE @LUCA
We rewrite the fluid problem under consideration, defined on a time-dependent domain, using the Arbitrary-Lagrangian-Eulerian (\ALE) formalism, which decouples the evolution of the computational domain from the evolution of the underlying fluid continuum. 
Let $\CompDomain_t$ be the computational domain where the fluid equations are solved at time $t$. We define the \ALE\ maps $\Alemap_t:\CompDomain_0 \to \CompDomain_t$ as the family of smooth and bijective functions that describe the evolution of the computational domain. These functions are defined through the extension of the displacement field at the boundary of the computational domain $\partial \CompDomain_t$ to the interior of $\CompDomain_t$. For instance, if $\bar{\phi}_t:\partial \CompDomain_0 \to \partial \CompDomain_t$ is the boundary displacement, a possible definition of the \ALE\ maps is $\Alemap_t(X) = X + \phi_t(X)$, for $X \in \CompDomain_0$, where $\phi_t(X)$ is the extension of $\bar{\phi}_t$ via
\begin{equation}
	\left\{
	\begin{aligned}
		&\nabla \cdot((1+\tau(X))\nabla \phi_t(X)) = 0, \quad &\text{on $\CompDomain_0$},\\
		&\mathcal{\phi}_t= \bar{\phi}_t, &\text{on $\partial \CompDomain_0$},
	\end{aligned}
	\right.
 \label{Eq: VarFormALE}
\end{equation}
where $\tau(X)$ acts as a space-dependent diffusion coefficient influencing the regions where larger displacements are localised.

>>>>

\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{xcolor}

@@

\newcommand{\review}[1]{\textcolor{blue}{#1}}

@@

\title*{Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact}
\titlerunning{\review{A computational framework for swimmers}}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Luca Berti, Laetitia Giraldi, Christophe Prud'homme, Céline Van Landeghem}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Luca Berti \at CNRS - Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg  \email{berti@math.unistra.fr}
\and Laetitia Giraldi \at Universit\'e C\^ote d'Azur, INRIA, CNRS, Calisto team, \email{laetitia.giraldi@inria.fr}
\and Christophe Prud'homme \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{christophe.prudhomme@math.unistra.fr}
\and Céline Van Landeghem \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{c.vanlandeghem@unistra.fr}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract{Swimming involves a body's capability to navigate through a fluid by undergoing self-deformations. Typically, fluid dynamics are described by the Navier-Stokes equations, and when integrated with a swimming body, it results in a highly intricate model. This paper introduces a computational framework for simulating the movement of multiple swimmers with various geometries immersed in a Navier-Stokes fluid. The approach relies on the finite element method with an Arbitrary Lagrangian-Eulerian (ALE) framework to handle swimmer displacements. Numerous numerical experiments demonstrate the adaptability of the computational framework across various scenarios.
All the implementations are made using the \feelpp\ finite element library \cite{feelpp-ref}.}

@@

Swimming involves the capacity of a body to navigate through a fluid by undergoing self-deformations. Typically, the fluid dynamics are described by the Navier-Stokes equations, and when coupled with a swimming body, it yields a highly intricate model. One of the main difficulties lies in the fact that the swimmers deform and move, requiring constant adjustment of the fluid domain and fluid-swimmer interface. Other difficulties come into play when accounting for obstacles, the possible presence of other swimmers, and the modeling of their interactions. These interactions are even more complex because disturbances caused by fluid agitation at one point in the domain can propagate throughout the entire domain.

@@

%BEM (Lefebvre - Maury - Kenta)
A numerical method that is widely used in the micro-swimming community is the boundary element method, that relies on the integral formulation of the Stokes equations to determine the fluid velocity field \cite{pozrikidis1992boundary}. 
This formulation reduces the \review{computational} cost of the dynamics of the swimmer by working on the swimmer's boundary alone, which ensures significant memory savings since the fluid domain is not discretized. 
The boundary integral formulation expresses the fluid velocity at the boundary of the swimmer as a function of fluid stresses and velocities, via the fundamental solutions of the Stokes equations. Since these functions exhibit singular behaviour when the source and evaluation points are close together, a regularisation procedure needs to be employed for the numerical solution. Several solutions are possible: a regularisation of the numerical approximation of the singular integrals using a semi-analytic procedure \cite{huang_cruse} or the use of regularised kernels \cite{Fauci}.

@@

% Méthode de frontière immergée
When inertial effects become more important and the low Reynolds number assumption is no longer valid, 
it is necessary to resort to the solution of the system coupling Navier-Stokes equations with Newton's equations for rigid bodies. 
A commonly used method involves approximating the values of fluid velocity and pressure on a fixed discretization of the domain and representing the swimmers using an implicit function that parameterizes their boundaries. 
These approaches are commonly referred \review{to as} Immersed Boundary Methods with level set functions describing the swimmer. 
The challenge of these methods lies in following the swimmer. 
For instance, one may use methods called CutFEM (Cut Finite Element Method), which project the swimmer's boundary onto the fixed mesh \cite{Monasse,Iollo,bergmann2016bioinspired,hansbo2016cut,burman2015cutfem}.
%\review{However, this approach is computationally costly.}
%the CUTFEM approach in which mesh intersections are computationally costly.

%[citer Laurent Monasse, Chouly, Iollo, Giocomini Matteo]

@@

% Méthode FEM-ALE
In this chapter, we discuss an alternative method to compute the displacement of multiple deformable swimmers immersed in a Navier-Stokes fluid, which can be confined within a geometrically complex domain. This method is based on the finite element solution of the swimming problem, using the Arbitrary-Lagrangian-Eulerian description for the motion of the fluid domain.
This approach is popular in fluid-structure interaction problems \cite{chabannes2013high,pena2012high}, and it is based on a formulation of the fluid equations in an intermediate frame between the Eulerian and Lagrangian description.
A characteristic of this method is that the solutions are approximated on a mesh that deforms over time, following the deformation and movements of the swimmers.
As the immersed boundary method, it accounts for the full, non-approximated description of the fluid dynamics.
%\review{Furthermore, when comparing this method to the CUTFEM method, in one instance, the high computational cost arises from projecting the swimmer onto the existing mesh, whereas in our case, the cost is associated with remeshing.}
This numerical method is very versatile and it has been used in a wide variety of contexts and physical problems, and it can be easily extended to cases in which the Newtonian fluid is substituted by a complex fluid, which is often the case of biological media.

@@

%Below, we present a dynamic system that describes the dynamics of a swimmer.
%la partie fluide :
We consider the Navier-Stokes equations in a moving domain to describe the motion of a Newtonian fluid medium. 
Let $\CompDomain_t\subset \R^d$, where $d=2,3$ is the dimension, denote the region occupied by the fluid at time $t$, $\mu$  the constant fluid viscosity and $\Density_\Fluid$ the constant fluid density. Let $\Solid_t^i \subset \R^d$ be the domain that is occupied by the body $i$, $i = 1,...,N$, where $N$ is the number of bodies, of constant density $\Density_\Solid^i$. At each time instant $t$, the fluid is in contact with the swimmers, and $\bar{\CompDomain}_{t} \cap \bar{\Solid}_t^i = \partial \Solid_t^i$.
The notations are summarized in Figure \ref{fig:swimmer-tikz}.

The velocity field $\Vel(t,x):]0,T]\times \CompDomain_t \rightarrow \R^d$ and the pressure field $\Pres(t,x):]0,T]\times\CompDomain_t \rightarrow \R$ satisfy the Navier-Stokes equations given by: 
\begin{equation}
	\begin{aligned}
		\rho_\Fluid \Big(\partial_t \Vel +( \Vel \cdot \nabla )\Vel \Big) \review{- \nabla \cdot \sigma(u,p)} &=  f%\nabla \cdot \Stress %\nabla \Pres + \Viscosity \Delta \Vel + f 
		\quad &\text{on $ ]0,T]\times \CompDomain_t$},
		\\
		\nabla \cdot \Vel &= 0  \quad&\text{on $ ]0,T]\times \CompDomain_t$},\\
		\Vel &= \bar{\Vel}^i% U + \Omega \times(x-\bar{x}) + u_d 
		\quad &\text{on $]0,T]\times \partial \Solid_t^i$},\\
		\Vel(0,x) &= \Vel_0(x) \quad &\text{on $ \{0\}\times\CompDomain_0$},\\
		\Vel(t,x) &= h(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,D}$},\\
		\sigma(u,p) \normal&=  g(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,N}$},
	\end{aligned}
	\label{Eq:NS}
\end{equation}
\review{where $\sigma(u,p)$ is the stress tensor $\sigma(u,p) = -\Pres\mathbb{I} + 2 \mu D(u)$, with $D(u) = \frac{1}{2}\left(\nabla u + (\nabla u)^T\right)$, and}
$\bar{\Vel}^i(t,x):[0,T]\times\partial \Solid_t^i \rightarrow \R^d$ results from the interaction between the fluid and the $i$-th swimmer's body and $f(t,x):[0,T]\times\CompDomain_t \rightarrow \R^d$ represents external volume forces. The function $u_0$ is the prescribed initial condition of the system. 
\begin{figure}
    \centering
\begin{center}
\begin{tikzpicture}

@@

\end{tikzpicture}
\end{center}
   \caption{Notations for the fluid-swimmer model. $\CompDomain_t$ denotes the fluid domain and $\Solid^i_t,\Solid^j_t,\Solid^k_t$ denote the swimmers and solid objects included in the fluid. $\partial \Fluid_{t,N}$ and $\partial \Fluid_{t,D}$ denote the portions of the fluid boundary where Dirichlet and Neumann boundary conditions are prescribed.}
    \label{fig:swimmer-tikz}
\end{figure}
Here $h(t,x)$ and $g(t,x)$ represent the Dirichlet and Neumann boundary conditions, prescribed on the respective portions of the fluid boundary $ ]0,T]\times\partial\CompDomain_{t,D}$ and  $ ]0,T]\times\partial\CompDomain_{t,N}$, and we have that $\partial \CompDomain_{t} = \partial\CompDomain_{t,D} \cup \partial\CompDomain_{t,N} \cup \partial \Solid_t^i$, $i=1,...,N$, for all times.

In the case of swimming, $\bar{\Vel}^i$ can be split into two contributions. The first one is determined by the linear velocity $\tvel^i(t): [0,T]\to\R^d$ and angular velocity  $\angvel^i(t):[0,T]\to \R^{d^*}$ of the swimmer around its center of mass $\CenterMassi$, where $d^*=1$ if $d=2$ and $d^*=3$ if $d=3$.  \review{The second one is given by the deformation velocity $u_d^i$, defined on the boundary of the swimmer. This latter models the swimming gait for active particles and vanishes for rigid bodies.} The function $\bar{u}^i$ then becomes $\bar{\Vel}^i(t,x) = \tvel^i(t) + \angvel^i(t)\times (x-\CenterMassi)+ \Vel_d^i(t)$.

%while the second one is given by the deformation velocity of the solid $\Vel_d^i$, if present.

@@

The swimmer's motion is either a result of external forces such as gravity and collision forces, or of its deformation, which generates hydrodynamic forces that are then translated into rigid movement through Newton's laws.
%, or external forces such as gravity or collision forces.

Let us define the mass of the $i$-th swimmer by  \review{$\mass^i = \int_{\Solid^i} \Density_{\Solid}^i$, where $\Solid^i = \Solid^i_0$ is the reference configuration}, %, let $\CenterMassi = \frac{1}{\mass^i} \int_{\Solid^i} \Density_{\Solid}^i x$ be its center of mass, 
and $\Inertia^i = \int_{\Solid^i} \Density_{\Solid}^i (x-\CenterMassi) \otimes (x-\CenterMassi)$ 
its positive definite and symmetric inertia tensor. 
The Newton and Euler equations describing the rigid body velocities $\tvel^i$ and $\angvel^i$ read:
\begin{equation}
	\begin{aligned}
		\mass^i \frac{d}{dt}\tvel^i &= F_e^i -\int_{\partial \Solid^i} \sigma \normal \,\textrm{ds},\\
		\frac{d}{dt}(\Rmat \Inertia^i \Rmat^T \angvel^i) &= T_e^i -\int_{\partial \Solid^i} \sigma \times (x-\CenterMassi)\,\textrm{ds}, 
	\end{aligned}
	\label{Eq:RB}
\end{equation}

where $\normal$ is the unit outward normal to $\partial \Solid^i$. \review{Equations \eqref{Eq:RB} correspond to the balance of forces and torques applied to each swimmer, stating that non-zero net contributions from fluid stresses $\sigma n$ or additional external forces $F_e^i$ and torques $T_e^i$ lead to velocity variations.}

The rotational speed $\angvel^i_k$ is linked with the orientation $R$ of the swimmer using

\begin{equation*}
	\begin{aligned}
		\frac{d}{dt} \Angle_k &= \angvel^i_k, \quad \text{for $k \in \{x,y,z\}$},\\
		\Rmat &=\Rmat_z(\Angle_z)\Rmat_y(\Angle_y)\Rmat_x(\Angle_x),
	\end{aligned}
\end{equation*}
where $R_k(\Angle_k)$ denotes the rotation matrix around axis $k \in \{x,y,z\}$ of 
angle $\Angle_k$. If $d=2$, $R(\theta)$ has the form: 
\begin{equation*}
	\begin{aligned}
		\Rmat(\Angle) &= \begin{bmatrix}
			\cos(\Angle) & \sin(\Angle)\\
			-\sin(\Angle) & \cos(\Angle)
		\end{bmatrix}.
	\end{aligned}
\end{equation*}
While in three dimensions:
$$	
	\Rmat_z(\Angle_z) = \begin{bmatrix}
		\cos(\Angle_z) & -\sin(\Angle_z) & 0\\
		\sin(\Angle_z) & \cos(\Angle_z)& 0 \\
		0& 0 & 1
	\end{bmatrix},
	\Rmat_y(\Angle_y) = \begin{bmatrix}
		\cos(\Angle_y) &0 & \sin(\Angle_y) \\
		0& 1& 0\\
		-\sin(\Angle_y) & 0& \cos(\Angle_y)
	\end{bmatrix},\\
$$
$$
	\Rmat_x(\Angle_x) = \begin{bmatrix}
		1 & 0 & 0\\
		0 &\cos(\Angle_x) & -\sin(\Angle_x) \\
		0 &\sin(\Angle_x) & \cos(\Angle_x) 
	\end{bmatrix}.
$$
The angle $\Angle$ belongs to  $\Theta$, with $\Theta = [-\pi,\pi]$ if $d=2$, 
or $\Angle_k \in \Theta$, $\Theta=[-\pi,\pi]\times[0,\pi]\times[0,\pi/2]$ if $d=3$.

@@

In this subsection, we describe how a swimmer's collisions with solid obstacles, other swimmers ,as active particles, and the boundaries of the fluid domain are handled. Our model is based on a short-range contact-avoidance repulsive force introduced by R. Glowinski in \cite{glowinski}. \review{The force is activated in a collision zone of width $w_{col}$}.
%for which a collision zone of width $\rho$ is defined in which the forces are activated.
In equation \eqref{Eq:RB}, the external force and torque terms $F_e^i$ and $T_e^i$ summarize the physical interactions occurring when the distances $d_{ij}$ and $d_{i}$ between swimmer $i$ and another body $j$, or between swimmer $i$ and the domain boundary $\partial \Fluid_t$, are smaller than the width \review{$w_{col}$} of the collision zone.  
The definition of the collision force for a swimmer-swimmer or swimmer-boundary pair is given by:

%$$
%\overrightarrow{F_{ij}} = - \epsilon A  \overrightarrow{X_i X_j }  1_{d_{ij} \leq \rho}, \qquad
%\overrightarrow{F_{i \partial \Fluid_t}} = - \epsilon' A \overrightarrow{X_i X_{\partial \Fluid_t} }  1_{d_{i} \leq \rho}.
%$$

\review{
$$
F_{ij} = - \epsilon A  ( X_j - X_i)  1_{d_{ij} \leq w_{col}}, \qquad
F_{i \partial \Fluid_t} = - \epsilon' A ( X_{\partial \Fluid_t} - X_i )  1_{d_{i} \leq w_{col}}.
$$}

@@

The total repulsion force applied on $\Solid^i$ is defined by:

%$$
%\overrightarrow{F_i} = \sum_{(i,j)|d_{ij} \leq \rho} %\overrightarrow{F_{ij}} +  \sum_{i | d_i \leq \rho} %\overrightarrow{F_{i \partial \Fluid_t}},
%$$

\review{
$$
F_e^i = \sum_{(i,j)|d_{ij} \leq w_{col}} F_{ij} +  \sum_{i | d_i \leq w_{col}} F_{i \partial \Fluid_t},
$$
}
where the first sum runs over all the body pairs $(i,j)$ such that $d_{ij}\le w_{col}$, and the second sum runs over all body-boundary pairs such that $d_{i}\le w_{col}$.

\review{ Force $F_e^i$ leads to body rotations via its associated torque, defined by: 
$$
T_e^i = - (X_i - x_{CM}^i )\times F_e^i,
$$
where  $X_i$ is the contact point where $F_e^i$ is applied.}

The total repulsion force and the external associated torque are added to the Newton equation \eqref{Eq:RB}, thus modifying the trajectory of the swimmer.

@@

\subsection{The Arbitrary-Lagrangian-Eulerian formalism}
% Introduire le framework ALE --- DONE @LUCA
The fluid problem defined on a time-dependent domain is solved using the Arbitrary-Lagrangian-Eulerian (\ALE) formalism, which allows to follow the evolution of the fluid-structure interface.
In the rest of this subsection, we set the number of swimmers to $N=1$ to avoid the complexity of the notation.

%decouples the evolution of the computational domain  %from the evolution of the fluid.

Let $\CompDomain_t$ be the current computational domain where the fluid equations are solved. 
We define the \ALE\ maps $\Alemap^t:\CompDomain_0 \to \CompDomain_t$ as the family of smooth and bijective functions that describe the evolution of the computational domain. 
These functions are defined through the extension of the displacement field at the boundary of the swimmer $\partial \mathcal{S}_t$ to the interior of $\CompDomain_t$.

For instance, if $\bar{\phi}^t:\partial \mathcal{S}_0 \to \partial \mathcal{S}_t$ is the boundary displacement, a possible definition of the \ALE\ maps is $\Alemap^t(X) = X + \phi^t(X)$, for $X \in \CompDomain_0$, where $\phi^t(X)$ is the extension of $\bar{\phi}^t$ via
\begin{equation}
	\left\{
	\begin{aligned}
		&\nabla \cdot((1+\tau(X))\nabla \phi^t(X)) = 0, \quad &\text{on $\CompDomain_0$},\\
		&\mathcal{\phi}^t= \bar{\phi}^t, &\text{on $\partial \mathcal{S}_0$},
	\end{aligned}
	\right.
 \label{Eq: VarFormALE}
\end{equation}
where $\tau(X)$ acts as a space-dependent diffusion coefficient influencing the regions where larger displacements are localised.

The time derivative of $\Vel$ in the \ALE\ frame can be expressed as a function of its Eulerian time derivative $\partial_t \Vel$ and the \ALE\ velocity $\Vel_{\mathcal{A}}(t,X)=\frac{\partial x}{\partial t}(t,(\Alemap^{t})^{-1}(x))$, $X \in \CompDomain_0$, which is the velocity of the moving domain:
\begin{equation}
\frac{\partial \Vel}{\partial t} \Big|_{\Alemap^t}(t,x)=\Vel_{\mathcal{A}} \cdot \nabla \Vel + \partial_t \Vel, \quad \text{$ x \in \CompDomain_t$}.
\end{equation}
